\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[top=0.60in,bottom=0.60in,left=0.70in,right=0.70in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[expansion=false]{microtype}
\usepackage{needspace}
\pagestyle{empty}
\raggedright
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\emergencystretch}{2em}
\setlist[itemize]{leftmargin=*, itemsep=1.8pt, topsep=2.5pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{0.06em}\hrule height 0.4pt]
\titlespacing*{\section}{0pt}{0.60em}{0.35em}
\newcommand{\jobentry}[4]{%
  \Needspace{3\baselineskip}%
  \textbf{#1} -- #2 \hfill \textit{#3}\\[-0.15em]
  \textit{#4}\\[-0.25em]
}
\newcommand{\projectentry}[3]{%
  \Needspace{3\baselineskip}%
  \textbf{#1} \hfill \textit{#2}\\[-0.15em]
  \textit{#3}\\[-0.25em]
}
\newcommand{\projectentryurl}[5]{%
  \Needspace{3\baselineskip}%
  \textbf{#1} \hfill \textit{#2}\\[-0.15em]
  {\small\href{#3}{\texttt{#4}}} \textbar\ \textit{#5}\\[-0.25em]
}
\begin{document}
%==================== HEADER ====================
\begin{center}
{\Large \textbf{Utkarsh Singh}}\\[0.04em]
{\normalsize Software Engineer (Full-Stack, Python, TypeScript/React, AI/LLM Applications, Cloud-Native)}\\[0.08em]
Dublin, Ireland \textbar\ +353 892515620 \textbar\ \href{mailto:254utkarsh@gmail.com}{254utkarsh@gmail.com}\\[0.08em]
\href{https://github.com/UT07}{github.com/UT07} \textbar\
\href{https://www.linkedin.com/in/utkarshsingh2001/}{linkedin.com/in/utkarshsingh2001} \textbar\
\href{https://utworld.netlify.app}{utworld.netlify.app}
\end{center}
\vspace{0.06em}
%==================== SUMMARY ====================
\section*{Summary}
Full-stack software engineer with \textbf{3+ years} of experience building, shipping, and operating scalable web applications and cloud-native services. Proficient in \textbf{Python} and \textbf{TypeScript/React} across the stack -- from designing RESTful APIs and data-driven backends to building responsive, component-based UIs. Experienced in integrating \textbf{AI/LLM capabilities} into production applications and working directly with customers to iterate in live environments. Strong foundation in data structures, algorithms, design patterns, and object-oriented architecture. Proven track record of owning features end-to-end -- from design through delivery -- with automated testing, CI/CD, and production-grade observability baked in. \textbf{MSc Cloud Computing}; \textbf{AWS Solutions Architect -- Professional}. Dublin-based (Stamp 1G) -- eligible for full-time employment in Ireland.
%==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, TypeScript/JavaScript, Java, SQL, Bash; familiar with Go, C++
  \item \textbf{Backend Frameworks:} FastAPI, Flask, Django, Node.js/Express, SQLAlchemy; REST API design, GraphQL, WebSocket, event-driven (SQS/SNS)
  \item \textbf{Front-End:} React 19, React Native, Tailwind CSS, Zustand/Redux, Framer Motion, Radix UI; component-based architecture, responsive design, state management, A/B testing
  \item \textbf{Databases:} PostgreSQL (Neon, RDS/Aurora), MySQL, DynamoDB, Redis, Firestore; query optimization, schema design, migrations (Alembic)
  \item \textbf{AI \& Data:} LLM integration (multi-model consensus, prompt engineering), ONNX inference, Gemini API, PySpark, data pipelines, ETL, API orchestration
  \item \textbf{Testing \& Quality:} Jest (3,000+ tests), Maestro (E2E), pytest, Playwright, JUnit, Selenium; SAST/DAST (SonarCloud, OWASP ZAP); code review, TDD
  \item \textbf{CI/CD \& DevOps:} GitHub Actions, Jenkins, AWS CodePipeline/CodeDeploy, Bitbucket Pipelines, EAS Build; automated test gates, blue/green and canary deployments
  \item \textbf{Cloud \& Infrastructure:} AWS (EC2, ECS/Fargate, EKS, Lambda, RDS, DynamoDB, S3, API Gateway, SQS/SNS, CloudFront, Route\,53, IAM), Firebase (Auth, Firestore, Functions), Supabase (Postgres, Auth, RLS), Docker, Kubernetes/Helm, Terraform
  \item \textbf{Observability:} Prometheus/Grafana, CloudWatch, PagerDuty, X-Ray, PostHog; SLO/SLI tracking, distributed tracing, incident response
  \item \textbf{Practices:} Git, Linux, design patterns, OOP, microservice architecture, agile/Scrum, GDPR compliance, API-first design
\end{itemize}
%==================== EXPERIENCE ====================
\section*{Experience}
\jobentry{Clover IT Services}{New York, NY (Remote)}{Jun 2022 -- Jul 2024}{\textbf{\textit{Software Engineer / Site Reliability Engineer}}}
\begin{itemize}
  \item Designed, developed, and maintained \textbf{8 production microservices} across a multi-region AWS SaaS platform; owned features end-to-end from requirements through implementation, testing, and production deployment.
  \item Built backend services in \textbf{Python} (FastAPI, Flask) and \textbf{Node.js}, implementing RESTful APIs, data orchestration layers, and event-driven integrations (SQS/SNS) across 3 AWS regions.
  \item Developed reusable front-end components and internal tooling UIs, collaborating with product managers to translate requirements into well-architected user experiences.
  \item Established \textbf{pytest and Jest test gates} across 10+ services in CI/CD pipelines; reduced release lead time from 3 days to \textbf{4--6 hours (85\% improvement)}.
  \item Architected full-stack observability (Prometheus/Grafana, CloudWatch, X-Ray) with SLO/SLI tracking; reduced \textbf{MTTR by 35\%} through proactive alerting and root cause analysis.
  \item Designed self-service infrastructure using Terraform modules and containerised deployments (Docker, EKS/Helm); sustained \textbf{99.9\% uptime} and delivered \textbf{22\% infrastructure cost reduction}.
  \item \textbf{Promoted to team lead within 14 months}; mentored 3--4 engineers, led design reviews, and championed engineering best practices.
\end{itemize}
\jobentry{Seattle Kraken (NHL)}{Seattle, WA}{Jun 2021 -- May 2022}{\textbf{\textit{Data Engineering Intern}}}
\begin{itemize}
  \item Built automated data pipelines in \textbf{Python} (PySpark, Azure Data Factory) for analytics ingestion and validation; reduced weekly report preparation time by \textbf{30\%} across 500K+ records supporting real-time dashboards.
  \item Developed internal reporting tools and interactive dashboards using \textbf{React} and D3.js, enabling non-technical stakeholders to self-serve analytics without engineering involvement.
  \item Implemented data quality checks catching \textbf{15+} silent data corruption incidents before production; partnered with engineering to debug ETL reliability and improve data freshness.
\end{itemize}
%==================== PROJECTS ====================
\section*{Featured Projects}
\projectentryurl{Purrrfect Keys -- AI Piano Learning App}{Jan 2026 -- Present}{https://expo.dev/accounts/ut254/projects/purrrfect-keys/builds/229bd252-c684-4af5-b39f-4f3623455a7e}{expo.dev/accounts/ut254/projects/purrrfect-keys}{React Native, TypeScript, Firebase, Gemini AI, ONNX, Jest, Maestro}
\begin{itemize}
  \item Shipped a cross-platform piano learning app through \textbf{14 development phases} with real-time pitch detection under \textbf{10ms}, AI-generated lessons via Gemini, competitive league with MMR ranking, and offline-first sync across 12 data types. \textbf{3,043 tests} passing across 149 suites.
  \item Designed the full architecture (React Native + Firebase + 9 Cloud Functions), built CI/CD with EAS Build, integrated PostHog analytics, and implemented gamification that drives daily active usage through cat avatar progression and streak rewards.
\end{itemize}
\vspace{0.20em}
\projectentryurl{WhatsTheCraic -- Live Event Discovery Platform}{Apr 2025 -- Jul 2025}{https://github.com/UT07/whatsthecraic}{whatsthecraic.run.place}{Node.js, React, FastAPI, MySQL, DynamoDB, Docker, AWS, Spotify OAuth}
\begin{itemize}
  \item Launched a live event platform that improved event discovery conversion by \textbf{18\%} through A/B-tested personalized ranking powered by Spotify listening data. Ingested events from Ticketmaster and Eventbrite with deduplication into a canonical data model.
  \item Designed and deployed \textbf{6 microservices} (aggregator, events, DJ, venue, auth, frontend) on AWS with Docker Compose, auto-TLS, and health/metrics instrumentation across 4 subdomains. Added ICS calendar export and Spotify OAuth for preference-based recommendations.
\end{itemize}
\vspace{0.20em}
\projectentryurl{Genomic Benchmarking Platform -- MSc Thesis}{Sep 2025 -- Dec 2025}{https://github.com/UT07/Performance-Optimization-and-Cost-Analysis-of-qpAdm-Genomic-Modeling}{github.com/UT07/qpAdm-Genomic-Benchmarking}{Terraform, Docker, Snakemake, EC2 Auto Scaling, S3, CloudWatch}
\begin{itemize}
  \item Ran \textbf{10,700+ parallel genomic workloads} on AWS with zero manual intervention. Terraform provisioned Auto Scaling Groups that launched workers, executed containerised jobs, emitted CloudWatch metrics, and self-terminated automatically.
  \item Cut compute costs by \textbf{66\%} using Spot Instances and eliminated \textbf{99\%} of preprocessing overhead through data precomputation. Found the optimal instance configuration at \textbf{\$0.006 per run}.
\end{itemize}
\vspace{0.20em}
\projectentryurl{Daily Job Hunt -- AI-Powered Job Automation SaaS}{Mar 2026 -- Present}{https://github.com/UT07/daily-job-hunt}{github.com/UT07/daily-job-hunt}{Python, FastAPI, React, Supabase, LaTeX, AWS Lambda, Playwright}
\begin{itemize}
  \item Automated the entire job search pipeline: scrapes \textbf{8 job boards} daily, scores candidates from 3 perspectives (ATS, Hiring Manager, Tech Recruiter) using a \textbf{consensus council of 24 LLMs}, generates tailored resumes and cover letters, and emails results with S3-hosted PDFs.
  \item Built as a multi-tenant SaaS: React dashboard with Supabase Auth and Row Level Security, GDPR-compliant data export/deletion, and a self-improvement loop that tracks per-model quality and deprioritizes underperforming AI models over time.
\end{itemize}
\vspace{0.20em}
\projectentryurl{UTWorld -- Dual-Mode Portfolio with CMS}{2024 -- Present}{https://utworld.netlify.app}{utworld.netlify.app}{React 19, FastAPI, SQLAlchemy, Neon PostgreSQL, AWS Lambda, S3, CloudFront}
\begin{itemize}
  \item Built a portfolio platform serving two distinct audiences (Professional and DJ) from a single codebase with mode switching, API-backed CMS, and an admin panel for managing projects, media, gigs, and resume uploads. S3 assets served via CloudFront CDN with static JSON fallback for resilience.
  \item Deployed as \textbf{3 independent services}: React 19 public site on Netlify, React 18 admin panel, and FastAPI REST API on AWS Lambda via SAM with CI/CD through GitHub Actions. Includes Pytest API tests and Playwright E2E coverage.
\end{itemize}
%==================== EDUCATION ====================
\section*{Education}
\textbf{National College of Ireland}, Dublin, Ireland \hfill \textit{Sep 2024 -- Jan 2026}\\[-0.15em]
\textbf{\textit{MSc Cloud Computing}}\\[-0.25em]
\begin{itemize}
  \item \textbf{Coursework:} Cloud Architectures, Cloud DevOpsSec, Scalable Cloud Programming, Cloud Machine Learning, Data Governance/Compliance/Ethics, Research in Computing.
\end{itemize}
\vspace{0.20em}
\textbf{Southern New Hampshire University}, Manchester, NH \hfill \textit{Aug 2023 -- May 2024}\\[-0.15em]
\textbf{\textit{BS Computer Science}}\\[-0.25em]
\begin{itemize}
  \item \textbf{Coursework:} Software Dev Lifecycle, Full-Stack Development, Database Systems, Software Testing.
\end{itemize}
\vspace{0.20em}
\textbf{The University of Texas at Arlington}, Arlington, TX \hfill \textit{Aug 2019 -- May 2022}\\[-0.15em]
\textbf{\textit{BS Software Engineering (Coursework, Transferred)}}\\[-0.25em]
\begin{itemize}
  \item \textbf{Coursework:} Algorithms \& DS, Operating Systems, Computer Networks, Information Security.
  \item \textbf{Teaching Assistant:} CSE 3318 Data Structures \& Algorithms (50+ students).
\end{itemize}
%==================== CERTIFICATIONS ====================
\section*{Certifications}
\begin{itemize}
  \item \href{https://www.credly.com/badges/6e22a6c0-9922-49d5-b59f-34cc593c82c3/public_url}{\textbf{\textit{AWS Certified Solutions Architect -- Professional (SAP-C02)}}} \hfill \textit{Issued Mar 2024}
  \item \href{https://www.credly.com/badges/84671bf4-ce9f-4d8b-a0de-0ef606ad5646/public_url}{\textbf{\textit{AWS Certified Developer -- Associate (DVA-C01)}}} \hfill \textit{Issued Sep 2022}
  \item \href{https://www.credly.com/badges/e671b9de-e72a-48cb-82fc-33776c285174/public_url}{\textbf{\textit{AWS Certified Cloud Practitioner (CLF-C01)}}} \hfill \textit{Issued Jun 2022}
\end{itemize}
\end{document}
